The title

### 2016-10-18 analysis/paper/paper.Rmd
more landscape observation

>>>>

According to Movius, two more terraces can be spotted from the river. After an intensive inspection, terrace 4 (T4) may be a cliff close to the river (base at 46 m) with a slight elevation  compared to the river (41 m). In contrast to the other terraces, the red gravel layer is absent on T4. However, the bedrock is overlain by  coarse gravels in a reddish brown sandy silt matrix (5 cm) that is followed by a reddish brown fine grained sandy silt with occasional small gravel clasts, as well as small carbonate modules.
